Effects of Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates on Sheath Blight of Rice

### 2020-08-12 analysis/paper/paper.Rmd
Edit statement about future design not being split plot

While the use of different levels of N did provide information about the effects of N on the disease, it reduced the statistical power to find the effects of the irrigation [@Bradley1998].
Using a high rate of N, _e.g._ 180&nbsp;k/ha, for the entire study would help ensure that enough disease occurs to be able to detect differences in the irrigation treatments with a more simple trial statistical design.

We would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the data.

>>>>

While the use of different levels of N did provide information about the effects of N on the disease, this effect was already known [@Castilla1996; @Tang2007], and it reduced the statistical power to find the effects in the main plot of the irrigation.
Designing a future experiment as a randomised complete block with two treatments, puddled or AWD and using a single high rate of N, _e.g._ 180&nbsp;k/ha would help ensure that disease occurs and increase the precision of measurements for the irrigation treatments.
Therefore, we would recommend that further future studies should focus only on the effects of AWD on sheath blight to gather data that provide a clear answer, while using the larger plot size and inoculation methods used in 2016 that improved the quality of data.
